Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Updated the Five Gaussian clusters section

  limits <- axis_param$limits
  axis_pos_x <- axis_param$axis_pos_x
  axis_pos_y <- axis_param$axis_pos_y
  threshold <- axis_param$threshold

  axes_obj <- gen_axes(  
    proj = projection,
    limits = limits,
    axis_pos_x = axis_pos_x,
    axis_pos_y = axis_pos_y,
    axis_labels = names(scaled_data),
    threshold = threshold)

@@

projected <- as.matrix(scaled_gau_data) %*% projection_scaled

projected_model <- as.matrix(scaled_gau_data_model) %*% projection_scaled

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.72,
  axis_pos_y = -0.72,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

projected <- as.matrix(scaled_gau_data) %*% projection

projected_model <- as.matrix(scaled_gau_data_model) %*% projection

axes_obj <- gen_axes(  
  proj = projection,
  limits = 1,
  axis_pos_x = -0.72,
  axis_pos_y = -0.72,
  axis_labels = names(scaled_gau_data),
  threshold = 0)

@@

@@

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2.5, 
               scaled_data = scaled_mnist_data, 
               scaled_data_model = scaled_mnist_data_model, 
               distance_df_small_edges = distance_df_small_edges_mnist, 
               axis_param = list(limits = 1, 
                                 axis_pos_x = -0.9, 
                                 axis_pos_y = -0.9, 
                                 threshold = 0.06))

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_mnist_data, 
               scaled_data_model = scaled_mnist_data_model, 
               distance_df_small_edges = distance_df_small_edges_mnist, 
               axis_param = list(limits = 1, 
                                 axis_pos_x = -0.83, 
                                 axis_pos_y = -0.83, 
                                 threshold = 0.06))

>>>>

  limits <- axis_param$limits
  axis_scaled <- axis_param$axis_scaled
  axis_pos_x <- axis_param$axis_pos_x
  axis_pos_y <- axis_param$axis_pos_y
  threshold <- axis_param$threshold

  axes_obj <- gen_axes(  
    proj = projection * axis_scaled,
    limits = limits,
    axis_pos_x = axis_pos_x,
    axis_pos_y = axis_pos_y,
    axis_labels = names(scaled_data),
    threshold = threshold)

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = distance_df_small_edges, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0))

projected_df <- proj_obj1$projected_df
model_df <- proj_obj1$model_df
axes <- proj_obj1$axes
circle <- proj_obj1$circle

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1, 
               scaled_data = scaled_gau_data, 
               scaled_data_model = scaled_gau_data_model, 
               distance_df_small_edges = distance_df_small_edges, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1,
                                 axis_pos_x = -0.72, 
                                 axis_pos_y = -0.72, 
                                 threshold = 0))

projected_df <- proj_obj1$projected_df
model_df <- proj_obj1$model_df
axes <- proj_obj1$axes
circle <- proj_obj1$circle

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 1.23, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = distance_df_small_edges_pbmc, 
               axis_param = list(limits = 1,
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.48, 
                                 axis_pos_y = -0.48, 
                                 threshold = 0.082))

projected_df <- proj_obj1$projected_df
model_df <- proj_obj1$model_df
axes <- proj_obj1$axes
circle <- proj_obj1$circle

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 1.25, 
               scaled_data = scaled_pbmc_data, 
               scaled_data_model = scaled_pbmc_data_model, 
               distance_df_small_edges = distance_df_small_edges_pbmc, 
               axis_param = list(limits = 1.35, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.75, 
                                 axis_pos_y = -0.75, 
                                 threshold = 0.12))

projected_df <- proj_obj2$projected_df
model_df <- proj_obj2$model_df
axes <- proj_obj2$axes
circle <- proj_obj2$circle

@@

proj_obj1 <- get_projection(projection = projection, 
               proj_scale = 2.5, 
               scaled_data = scaled_mnist_data, 
               scaled_data_model = scaled_mnist_data_model, 
               distance_df_small_edges = distance_df_small_edges_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.9, 
                                 axis_pos_y = -0.9, 
                                 threshold = 0.06))

@@

proj_obj2 <- get_projection(projection = projection, 
               proj_scale = 2, 
               scaled_data = scaled_mnist_data, 
               scaled_data_model = scaled_mnist_data_model, 
               distance_df_small_edges = distance_df_small_edges_mnist, 
               axis_param = list(limits = 1, 
                                 axis_scaled = 1, 
                                 axis_pos_x = -0.83, 
                                 axis_pos_y = -0.83, 
                                 threshold = 0.06))
